A free/open-source Kazakh-Tatar machine translation system

### 2013-04-06 paper/paper.tex
MUCH BETTAR

\documentclass[11pt,a4paper]{article}
\usepackage{mtsxiv}
%\usepackage{url}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}
%\usepackage{times}
\usepackage{multirow}
\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}
\usepackage{latexsym}
\usepackage[small,bf]{caption}
\usepackage{xltxtra}

@@

@@

\abstract{
This paper presents a bidirectional machine translation system between
Kazakh and Tatar.
 \\
%FIXME
%\Keywords{Kazakh, Tatar, MT, Free software, Open-source}
}

\begin{document}
\spacing{1}
%FIXME
%\maketitleabstract

@@

%\bibliographystyle{lrec2012}
%\bibliography{tt-ba}
\bibliographystyle{apa}
\bibliography{paper}

>>>>

\documentclass[11pt]{article}

\usepackage{mtsxiv}
%\usepackage{url}
\usepackage[colorlinks=true,citecolor=black,linkcolor=black,urlcolor=blue]{hyperref}
%\usepackage{times}
\usepackage{multirow}
\setlength\titlebox{6.5cm}    % Expanding the titlebox

\usepackage{polyglossia}
\setdefaultlanguage[variant=australian]{english}
\usepackage{latexsym}
\usepackage[small,bf]{caption}
\usepackage{xltxtra}

@@

%\abstract{
%This paper presents a bidirectional machine translation system between
%Kazakh and Tatar.
% \\
%%FIXME
%%\Keywords{Kazakh, Tatar, MT, Free software, Open-source}
%}

\newcommand{\confname}{Machine Translation Summit XIV}
\newcommand{\website}{\protect\url{http://www.mtsummit2013.info/}}
\newcommand{\contactname}{research track co-chair Mikel L.\ Forcada}
\newcommand{\contactemail}{mlf@dlsi.ua.es} 
\newcommand{\conffilename}{mtsxiv}
\newcommand{\downloadsite}{\protect\url{http://www.mtsummit2013.info/}}
\newcommand{\paperlength}{$8$ (eight)}
\newcommand{\shortpaperlength}{$4$ (four)}

\author{Ilnar Salimzyanov\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  {\tt email@domain}  \And
  Jonathan North Washington\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  {\tt email@domain}  \And
  Francis Morton Tyers\\
  Affiliation / Address line 1\\
  Affiliation / Address line 2\\
  Affiliation / Address line 3\\
  {\tt email@domain}}

@@

\begin{document}
\spacing{1}
\maketitle
\begin{abstract}
This paper presents a bidirectional machine translation system between Kazakh and Tatar.
\end{abstract}
%FIXME
%\maketitleabstract

@@

%\bibliographystyle{lrec2012}
%\bibliography{tt-ba}
\bibliographystyle{mtsxiv}
\bibliography{paper}
